---
title: "Notes! Day 1"
author: "Liz Roten"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(usethis)
```


Materials - https://github.com/rstudio-conf-2022/pkg-dev-masterclass

## Notes!

checklists!

```{r, eval=F}
use_tidy_upkeep_issue()
```


### `{usethis}` standards

- `usethis::use_tidy_style()`
- 

### Testing

Use a `devtools::load_all()` workflow. (CMD + Shift + L)

1. Test should be self-sufficient and self-contained
1. Interactive workflow is very important. USE THE STANDARD WORKFLOW
1. Obvious >>> DRY (do not repeat yourself)
    - make it super obvious why it works
    - when you are working on on a failing test, you are already in a bad mood, so make it super easy to review
1. Don'
    - what that is causing you to do in your test suite
    - is it leaving a lot of junk?
1. Pull the object creation *inside* `test_that()`, which put everything in its own little environment

think about if someone else would see if they parachute in
Using the official 
- `withr::local_options()` -> does something and schedules its destruction
- do not run `library()` or `source()` within /tests
 - make tests/fixtures/
 
 setup.R is not run by `load_all()`. Use it for CI setup, etc
 only write to session temp.dir, and clean up after yourself
 
 
